Summary of Performance Measures for Scenario OR

### 2024-08-22 doc/performance.Rmd
fixed some error / edit Performance.Rmd, PerformanceER.Rmd, PerformanceOR.Rmd

```{r data}
library(rsimsum)
library(dplyr)
library(tidyr)
library(kableExtra)

@@

est$model <- as.factor(est$model)
levels(est$model) <- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward")
levels <- levels(est$model)
```

@@

```{r plots, warning=FALSE, message=FALSE}
require(ggplot2)

custom_theme <- theme_minimal() + 
  theme(
    panel.background = element_rect(fill = "white"),  
    panel.grid.major = element_blank(),              
    panel.grid.minor = element_blank(),              
    legend.position = "bottom"                      
  )

@@

```{r plotSE, warning=FALSE, message=FALSE}
library(reshape2)
library(tidyr)

data <- s1$summ %>%
  filter(stat %in% c("empse", "modelse")) %>%
  select(model, stat, est) %>%
  pivot_wider(names_from = stat, values_from = est)

>>>>

```{r data}
library(rsimsum)
library(dplyr)
library(tidyr)
library(kableExtra)
library(reshape2)
library(ggplot2)

@@

est$model <- as.factor(est$model)
levels<- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward")
est$model <- factor(est$model, levels = levels)
levels(est$model)
```

@@

```{r plots, warning=FALSE, message=FALSE}
custom_theme <- theme_minimal() + 
  theme(
    panel.background = element_rect(fill = "white"),  
    panel.grid.major = element_blank(),              
    panel.grid.minor = element_blank(),              
    legend.position = "bottom"                      
  )

@@

```{r plotSE, warning=FALSE, message=FALSE}
data <- s1$summ %>%
  filter(stat %in% c("empse", "modelse")) %>%
  select(model, stat, est) %>%
  pivot_wider(names_from = stat, values_from = est)

### 2024-08-22 doc/performanceER.Rmd
fixed some error / edit Performance.Rmd, PerformanceER.Rmd, PerformanceOR.Rmd

ind <- which(!is.na(RD_bross[,1]))

est_bross    <- RD_bross[ind,]
est_hybird   <- RD_hybrid[ind,]
est_lasso    <- RD_lasso[ind,]
est_enet     <- RD_enet[ind,]
est_ga       <- RD_ga[ind,]
est_xgboost  <- RD_xgboost[ind,]
est_rf       <- RD_rf[ind,]
est_forward  <- RD_forward[ind,]
est_backward <- RD_backward[ind,]

>>>>

ind <- which(!is.na(RD_bross.ER[,1]))

est_bross    <- RD_bross.ER[ind,]
est_hybird   <- RD_hybrid_ER[ind,]
est_lasso    <- RD_lasso_ER[ind,]
est_enet     <- RD_enet_ER[ind,]
est_ga       <- RD_ga_ER[ind,]
est_xgboost  <- RD_xgboost_ER[ind,]
est_rf       <- RD_rf_ER[ind,]
est_forward  <- RD_forward[ind,]
est_backward <- RD_backward[ind,]

### 2024-08-22 doc/performanceOR.Rmd
fixed some error / edit Performance.Rmd, PerformanceER.Rmd, PerformanceOR.Rmd

ind <- which(!is.na(RD_bross[,1]))

est_bross    <- RD_bross[ind,]
est_hybird   <- RD_hybrid[ind,]
est_lasso    <- RD_lasso[ind,]
est_enet     <- RD_enet[ind,]
est_ga       <- RD_ga[ind,]
est_xgboost  <- RD_xgboost[ind,]
est_rf       <- RD_rf[ind,]
est_forward  <- RD_forward[ind,]
est_backward <- RD_backward[ind,]

@@

```{r bind}
est <- rbind(est_bross, est_hybird, est_lasso, est_enet, 
             est_ga, est_xgboost, est_rf,
             est_forward, est_backward)

est$model <- as.factor(est$model)
levels(est$model) <- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward")
levels <- levels(est$model)
```

>>>>

ind <- which(!is.na(RD_bross.OR[,1]))

est_bross    <- RD_bross.OR[ind,]
est_hybird   <- RD_hybrid_OR[ind,]
est_lasso    <- RD_lasso_OR[ind,]
est_enet     <- RD_enet_OR[ind,]
est_ga       <- RD_ga_OR[ind,]
est_xgboost  <- RD_xgboost_OR[ind,]
est_rf       <- RD_rf_OR[ind,]
est_forward  <- RD_forward[ind,]
est_backward <- RD_backward[ind,]

@@

```{r bind}
est <- rbind(est_bross, est_hybird, est_lasso, est_enet, 
             est_ga, est_xgboost, est_rf,
             est_forward, est_backward)
est$model <- as.factor(est$model)
levels<- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward")
est$model <- factor(est$model, levels = levels)
levels(est$model)
```
